Community Embeddings with Bayesian Gaussian Mixture Model and Variational Inference\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2022-05-21 paper-ComE-BGMM-VI.tex
🧹 cleanup

The advantage of a smaller embedding becomes clearer for larger values of $K>K^*$. For $K=20$ the NMI for the 128-dimensional embedding is around $0.3$, while the BGMM two-dimensional embedding manages to hold at $0.45$.

@@

To understand why ComE BGMM+VI is able to maintain an NMI score for larger values of $K$ for the two-dimensional embedding, but not for the 128-dimensional embedding, the weights of the components for $K=20$ is presented:

\begin{figure}[H]
    \centering
    % K=5
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d2_k5.png}
        \caption{D=2, K=5}
        \label{fig:dblp_weights_d2_k5}
    \end{subfigure}%
    %
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d128_k5.png}
        \caption{D=128, K=5}
        \label{fig:dblp_weights_d128_k5}
    \end{subfigure}
    % K=10
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d2_k10.png}
        \caption{D=2, K=10}
        \label{fig:dblp_weights_d2_k10}
    \end{subfigure}%
    %
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d128_k10.png}
        \caption{D=128, K=10}
        \label{fig:dblp_weights_d128_k10}
    \end{subfigure}
    % K=20
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d2_k20.png}
        \caption{D=2, K=20}
        \label{fig:dblp_weights_d2_k20}
    \end{subfigure}%
    %
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d128_k20.png}
        \caption{D=128, K=20}
        \label{fig:dblp_weights_d128_k20}
    \end{subfigure}

>>>>

The potential advantage of a smaller embedding becomes clearer for larger values of $K>K^*$. For $K=20$ the NMI for the 128-dimensional embedding is around $0.3$, while the BGMM two-dimensional embedding manages to hold at $0.45$.

@@

\begin{figure}
    \centering
    % K=5
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d2_k5.png}
        \caption{D=2, K=5}
        \label{fig:dblp_weights_d2_k5}
    \end{subfigure}%
    %
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d128_k5.png}
        \caption{D=128, K=5}
        \label{fig:dblp_weights_d128_k5}
    \end{subfigure}
    % K=10
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d2_k10.png}
        \caption{D=2, K=10}
        \label{fig:dblp_weights_d2_k10}
    \end{subfigure}%
    %
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d128_k10.png}
        \caption{D=128, K=10}
        \label{fig:dblp_weights_d128_k10}
    \end{subfigure}
    % K=20
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d2_k20.png}
        \caption{D=2, K=20}
        \label{fig:dblp_weights_d2_k20}
    \end{subfigure}%
    %
    \begin{subfigure}[b]{.5\linewidth}
        \centering
        \includegraphics[width=1\linewidth]{images/eval/weights_BGMM_d128_k20.png}
        \caption{D=128, K=20}
        \label{fig:dblp_weights_d128_k20}
    \end{subfigure}
